Response to the defense feedback

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

In contrast, an \emph{average} estimate based on random secret input information is around 1 bit, as shown in the previous section and Table~\ref{shtable}, is not very useful in practice as an attacker is able to get much more leaked
information in some attack scenarios.

@@

\section{Approximate Model Counting}
\label{MCreasons}
In the previous section, we propose an information leakage definition for realistic attack scenarios to model two types of address-based side-channel leakages and showed how to quantify them by calculating the number of input keys ($K^o$) that satisfy the formulas. Intuitively, we can use symbolic execution to capture math formulas and model counting to obtain the number of satisfying input keys ($K^o$). However, some preliminary experiments showed that this approach was far too expensive to use with real-world applications. In this section, we discuss the bottlenecks in this approach and propose a practical solution.

>>>>

In contrast, an \emph{average} estimate based on random secret input information is around $1$ bit, as shown in the previous section and Table~\ref{shtable}, is not very useful in practice as an attacker is able to get much more leaked
information in some attack scenarios. As the size of input-sensitive information is
usually public, the problem of quantifying the leaked information is equivalent to the problem of estimating the size of input key $|K^o|$ under
the condition $o \in O$.

@@

\section{Approximate Model Counting}
\label{MCreasons}
In the previous section, we propose an information leakage definition for realistic attack scenarios to model two types of address-based side-channel leakages and show how to quantify them by calculating the number of input keys ($K^o$) that satisfy the formulas. Intuitively, we can use symbolic execution to capture math formulas and model counting to obtain the number of satisfying input keys ($K^o$). However, some preliminary experiments showed that this approach was far too expensive to use with real-world applications. In this section, we discuss the bottlenecks in this approach and propose a practical solution.
